\replaced{Fast Fourier transformation of electromagnetic data for computationally expensive kernels}{Fast time-domain electromagnetic modelling in the frequency domain}

### 2020-11-27 ManuscriptTime.tex
EOD

\documentclass[onecolumn,extra,referee,camera]{gji}
% \documentclass[onecolumn,extra,camera]{gji}
% \documentclass[twocolumn,extra,camera]{gji}
\usepackage{timet}

% Additional packages
% \usepackage[UKenglish]{babel}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{amssymb, amsmath, amsfonts}
\usepackage{booktabs}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage[position=top]{subfig}
\usepackage{ifthen}
\usepackage[draft, addedmarkup=bf]{changes}
% \usepackage[final]{changes}
\usepackage[pdftex, final, allcolors=blue, colorlinks=true]{hyperref}

@@

\title[\replaced{Transform for expensive EM kernels}{Time-domain CSEM}]{
  \replaced{Fast Fourier transformation of electromagnetic data for expensive kernels}{Fast time-domain electromagnetic modelling in the frequency domain}}

@@

\begin{document}
\large %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TODO %%%

@@

\begin{summary}
%
Modelling three-dimensional time-domain controlled-source electromagnetic data
with frequency-domain solvers is an alternative to time-domain solvers. It
requires the computation of many frequencies if standard Fourier transforms are
used, which can make it prohibitively expensive in comparison with a
time-domain computation. The speed of time-domain modelling with
frequency-domain computation is defined by three key points: solver, method and
implementation of the Fourier transformation, and gridding.
%
The faster the frequency-domain solver, the faster time-domain modelling will
be. It is important that the solver is robust over a wide range of frequencies.
A three-dimensional, iterative, frequency-domain multigrid solver satisfies
this requirement, but any other robust solver will do.
%
The method should require as few frequencies as possible while remaining
robust. As the frequency range spans many orders of magnitude, the required
frequencies are ideally equally spaced on a logarithmic scale. The fast
frequency-to-time domain method uses either the digital linear filter method
or the logarithmic fast Fourier transform together with a careful selection of
frequencies and interpolation. This methodology requires typically 15 to 20
frequencies to cover a wide range of offsets\deleted{in one-dimensional test
models}.
%
The gridding should be frequency-dependent, which is accomplished by making it
a function of skin depth. Optimising for the least number of required cells for
a given frequency should be combined with optimising for computational speed.
%
Looking carefully at these \deleted{three} points results in much smaller
computation times with speedup factors of ten or more over previous results. A
frequency-domain computation of time-domain data can therefore be competitive
to time-domain solvers if the required frequencies and the corresponding grids
are carefully chosen.
%
\end{summary}

>>>>

\documentclass[extra, camera,%
    % onecolumn,   % comment for two columns
    referee,     % uncomment for double lines
    % final,       % uncomment for changes
]{gji}
\usepackage{timet}

% Additional packages
% \usepackage[UKenglish]{babel}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage{amssymb, amsmath, amsfonts}
\usepackage{booktabs}
\usepackage{xspace}
\usepackage[final]{graphicx}
\usepackage[position=top]{subfig}
\usepackage{ifthen}
\usepackage[addedmarkup=bf]{changes}
% \usepackage[final]{changes}
\usepackage[pdftex, final, allcolors=blue, colorlinks=true]{hyperref}

@@

\title[\replaced{Transforming expensive EM kernels}{Time-domain CSEM}]{
  \replaced{Fast Fourier transformation of electromagnetic data for
  computationally expensive kernels}{Fast time-domain electromagnetic modelling
  in the frequency domain}}

@@

\begin{document}

@@

\begin{summary}
%
\deleted{Modelling three-dimensional time-domain controlled-source
electromagnetic data with frequen\-cy-domain solvers is an alternative to
time-domain solvers.} \added{Three-dimensional controlled-source
electromagnetic data is often computed directly in the domain of interest,
either in the frequency domain or in the time domain. Computing it in one
domain and transforming it via a Fourier transform to the other domain is a
viable alternative.} It requires the \replaced{evaluation}{computation} of many
\replaced{responses in the computational domain}{frequencies} if standard
Fourier transforms are used, which can make it prohibitively expensive\deleted{
in comparison with a time-domain computation}. The speed of
\replaced{such}{time-domain} modelling \replaced{which is followed by a
transform}{with frequency-domain computation} is defined by three key points:
solver, method and implementation of the Fourier transformation, and gridding.
%
The faster the \deleted{frequency-domain} solver, the faster
\deleted{time-domain} modelling will be. It is important that the solver is
robust over a wide range of \added{values (}frequencies\added{ or times)}.
\deleted{A three-dimensional, iterative, frequency-domain multigrid solver
satisfies this re\-quirement, but any other robust solver will do.}
%
The method should require as few \replaced{kernel evaluations}{frequencies} as
possible while remaining robust. As the frequency \added{and time}
range\added{s} span\deleted{s} many orders of magnitude, the required
\replaced{values}{frequencies} are ideally equally spaced on a logarithmic
scale. The \added{proposed} fast \deleted{frequency-to-time domain} method uses
either the digital linear filter method or the logarithmic fast Fourier
transform together with a careful selection of \replaced{evaluation
points}{frequencies} and interpolation. \replaced{In frequency-to-time domain
tests t}{T}his methodology requires typically 15 to 20 frequencies to cover a
wide range of offsets\deleted{in one-dimensional test models}.
%
The gridding should be frequency-\added{ or time-}dependent, which is
accomplished by making it a function of skin depth. Optimising for the least
number of required cells \deleted{for a given frequency} should be combined
with optimising for computational speed.
%
Looking carefully at these \deleted{three} points results in much smaller
computation times with speedup factors of ten or more over previous results. A
\deleted{frequency-domain} computation \replaced{followed by transformation}{of
time-domain data} can therefore be competitive to \replaced{computation in the
required }{time-}domain \deleted{solvers} if the required \replaced{evaluation
points}{frequencies} and the corresponding grids are carefully chosen.
%
\end{summary}
